### 2018-10-09 Sections/essay_to_the_future_QKD.tex
Minor tweaks, formatting

\section{The future of quantum key distribution}

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike the current cryptography system which is based on the limit of computational power of an adversary, the security of QKD only assume the laws of physics, and a correct implementation.

The typical setting of QKD is as follows. The two trusted parties who want to establish a secret key are typically named Alice and Bob. They share two channels, a quantum channel, which allows them to send quantum state to one another, and a classical channel, with which they can send classical messages. The communication over the classical channel is assume to be public, and the eavesdropper (Eve) has free access to without  ever being detected, however, Eve cannot modify the messages shared over the classical channel.

The quantum channel is subjected to possible manipulation from an eavesdropper. The task of Alice and Bob is thus to guarantee security against an adversarial eavesdropper. The typical protocol assumes that Alice and Bob do not share any secret to begin with. The origin of the security of QKD springs from the fundamentals of quantum mechanics, that is, any action by an observer on a quantum state necessarily induces a change in the state. This means that in combination with classical communication, actions of an eavesdropper cannot go undetected.

@@

Despite the significant advances in both the theoretical and experimental development of QKD, a number of challenges remain for QKD to be widely used  in securing daily communications \cite{bib:RevModPhys.81.1301, bib:diamanti2016practical}. Experimentally, much effort is being put into improving the performance of the QKD system. On the theory side,  showing the security of a QKD system with finite key size is also a challenge,   because information-theoretic security is achieved only when immunity against the most general (coherent) attack is proven \cite{bib:diamanti2016practical}.

@@

Some of the criteria for assessing the performance of a QKD scheme include key rate, distance, cost and robustness.

Keyrate - currently, a strong disparity exists between classical and quantum key distribution rates. Classical optical communication delivers in the order of 100 Gbits per second per wavelength, whereas Mbit/s rates are achieved with QKD.

The obtained key rate depends on the performance of the detector used. For QKD based on single-photon detection techniques, to achieve a high bit rate, one requires true single-photon states, in combination with detectors with high efficiency and short dead time. The current developments are promising, with a reported quantum efficiency of $93\%$ at telecom wavelengths \cite{bib:marsili2013detecting}.

@@

Distance-extending the range of QKD systems is a major challenge and driving factor for QKD in terms of future network applications. Basically, two approaches are being pursued -- free space and repeaters.  A quantum repeater, similar to its classical analogue, is a device that can extend the range of quantum communication between sender and receiver. However, one cannot amplify the signal that contains the quantum information, which we know from the no-cloning theorem. The no-cloning theorem states that one cannot make copies of an unknown quantum state whilst leaving the original one unchanged, which is the basis of the security of QKD.

A quantum repeater effectively needs to restore the quantum information without measuring it directly, and is a component which is extremely technologically challenging. Over optical fibre networks, the standard loss for 1550 nm is 0.2 dB/km. Over enough distance, this unavoidable loss will reduce the key rate to a level of little practical relevance, therefore a ground-based solution would be to divide the entire channel into segments, where two partners exchange pairs of entangled photons and store it in a quantum memory \cite{bib:PhysRevLett.81.5932, bib:PhysRevA.59.169}.

The second is to use free space quantum communication techniques via satellite links. Satellite QKD is reachable with the present technology. Here satellites are used as intermediate trusted nodes for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances. Satellite QKD suffers less loss, because the quantum channel is mostly free-space once $\approx$ 10 km above sea level.

In China, satellite QKD over 1200 km has been demonstrated \cite{bib:liao2017satellite}.

Cost and robustness - 
For QKD systems to be consumer-friendly, low cost and robustness are crucial features. Preferably QKD systems should make use of existing data fibre-optic infrastructure since the use of dark fibres are not only expensive, but often unavailable \cite{bib:diamanti2016practical}. Single-photon detectors at room temperatures are also desirable,  because this can remove the requirement for cryogenic cooling, hence reduces power consumption.

@@

Currently, two platforms are being explored, silicon \cite{bib:lim2014review} and indium phosphide \cite{bib:smit2014introduction}. A reconfigurable QKD system which uses an In-P transmitter and silicon detectors has been demonstrated in the laboratory \cite{bib:sibson2017chip}.

@@

In parallel to hardware development, research effort is directed at finding new QKD protocols which can out-perform the existing ones. Two of these are high-dimensional (HD) QKD and the Round-Robin differential phase shift protocol (RR-DPS).

High-dimensional QKD aims at encoding more than one bit in each detected photon, which can increase the information capacity when the photon rate is limited. Security proof against collective attacks are being developed, and an experiment has demonstrated an information capacity 6.9 bits per coincidence rate at 2.7Mbit/s over 20km \cite{bib:zhong2015photon}.

@@

Although QKD protocols can be proven to be secure from an information-theoretic perspective, physical implementations often contain imperfections which are not considered in the model. Attacks can be designed to exploit such imperfections, on either the source or the detectors.

Tab.~\ref{attacks} (from \cite{bib:lo2014secure}) summarises some attacks against certain commercial and research systems.

\startnormtable
\begin{table*}[!htbp]
\begin{tabular}{ |c|c|c|c| } 
 \hline
 Attack &  Targeted component & Tested system & References\\ 
  \hline
  \hline
Time shift
        & Detector & Commercial & \cite{bib:qi2005time, bib:PhysRevA.78.042333, bib:PhysRevA.74.022313}\\
Time information & Detector & Research & \cite{bib:lamas2007breaking} \\
Detector control & Detector  &   Commercial & \cite{bib:lydersen2010hacking, bib:yuan2010avoiding}\\
Detector control  & Detector  & Research & \cite{bib:gerhardt2011full} \\
Detector dead-time      & Detector  & Research   & \cite{bib:weier2011quantum}      \\
Channel calibration    & Detector  &  Commercial  & \cite{bib:jain2011device}      \\
Phase remapping  &  Phase modulator & Commercial & \cite{bib:xu2010experimental} \\
Phase information & Source & Research & \cite{bib:tang2013source}          \\
Device calibration  & Local oscillator & Research & \cite{bib:jouguet2013preventing} \\
                \hline
\end{tabular}
\caption{\label{attacks} Summary of various attacks against some commercial and 
research QKD systems}
\end{table*}
\startalgtable

To regain security, a number of solutions have been proposed.

QKD with imperfect sources -- the source is typically less vulnerable to attacks because Alice can prepare her quantum states in a protected environment, and we expect that she can characterise her source. Therefore flaws in the state preparation can be incorporated into the security proof.

A loss-tolerant protocols has been proposed \cite{bib:PhysRevA.90.052314}, and further developed by \cite{bib:PhysRevA.92.032305}, where decoy-state QKD with tight finite-key security has been employed. A wide range of imperfections with the laser source has been taken into account in \cite{bib:mizutani2015finite}, including intensity fluctuation. A security proof has shown that perfect phase randomisation is also not necessary \cite{bib:cao2015discrete}.

These are strong evidence which suggests that secure quantum communication with imperfect sources is feasible \cite{bib:diamanti2016practical}. Intuitively, QKD with imperfect sources are feasible, because by assuming that the states prepared by Alice are qubits, then Eve cannot unambiguously discriminate Alice's states \cite{bib:diamanti2016practical}.

Measurement-device-independent QKD -

To prove security for Bob's measurement device is more problematic, since Eve has complete access to the quantum channel and she can send in any signal.

One candidate for a long-term solution to side-channel attacks is device-independent (DI) QKD \cite{bib:PhysRevLett.98.230501}. It relies on the violation of a Bell inequality \cite{bib:hensen2015loophole}, and the security can be proven without knowledge of the implementation. However, the expected secure key rate is low even at short distances. A more practical approach is measurement-device independence (MDI) \cite{bib:PhysRevLett.108.130503}, which is immune to side-channel attacks against the measurement device. Here the device is treated as a black box, and does not need to be trusted. An important assumption for MDI QKD is that Eve cannot interfere with the state preparation process.

@@

We have discussed some significant remaining challenges in QKD. These range from theoretical security proofs to hardware developments. Advances in QKD will not only enable point-to-point quantum communication, but have implications for a range of network applications, such as quantum secret sharing \cite{bib:cleve1999share, bib:PhysRevA.61.042311, bib:PhysRevA.71.044301}, blind quantum computing \cite{bib:broadbent2009universal, bib:barz2012demonstration}, quantum anonymous broadcasting \cite{bib:christandl2005quantum} and more.

>>>>

\section{The future of quantum cryptography}\label{sec:essay_future_QKD}\index{Quantum key distribution (QKD)}\index{Quantum cryptography}

\dropcap{Q}{uantum} key distribution (QKD) is the first quantum information task to reach commercialisation. Its purpose is to distribute a secret key between two trusted parties who share a quantum channel, as well as a classical channel for authentication. Unlike current cryptography systems, which are secure based on the limitations of an adversary's computer (\textit{computational security}\index{Computational security}), the security of QKD is based on the laws of quantum mechanics, providing guaranteed security unless our understanding of quantum physics is inherently wrong (\textit{information theoretic security}\index{Information theoretic security}).

The typical setting of QKD is as follows. The two trusted parties who want to establish a secret key are typically named Alice and Bob. They share two channels: a quantum channel, which allows them to send quantum state to one another; and, a classical channel, with which they can send classical messages. The communication over the classical channel is assume to be public, and the eavesdropper (Eve) has full anonymous access to it. However, Eve cannot modify messages shared over the classical channel.

The quantum channel is subject to possible manipulation by Eve. The task of Alice and Bob is thus to guarantee security against an adversarial eavesdropper. The typical protocol assumes that Alice and Bob do not share any secret to begin with. The origin of the security of QKD springs from the fundamentals of quantum mechanics, that is, any action by an observer on a quantum state necessarily induces a change in the state. This means that in combination with classical communication, actions of an eavesdropper cannot go undetected.

@@

Despite the significant advances in both the theoretical and experimental development of QKD, a number of challenges remain for QKD to be widely used in securing daily communications \cite{bib:RevModPhys.81.1301, bib:diamanti2016practical}. Experimentally, much effort is being invested into improving the performance of QKD systems. On the theory side,  showing the security of a QKD system with finite key size is also a challenge, because information-theoretic security is achieved only when immunity against the most general (coherent) attack is proven \cite{bib:diamanti2016practical}.

@@

Some of the criteria for assessing the performance of a QKD scheme include key-rate, distance, cost and robustness.

\subsubsection{Key-rate}

Currently, a strong disparity exists between classical and quantum key distribution rates. Classical optical communication delivers in the order of 100Gbits/second per wavelength, whereas communication rates only on the order of Mbit/s are achieved with QKD.

The obtained key-rate depends on the performance of the detector used. For QKD based on single-photon detection techniques, to achieve a high bit-rate, one requires true single-photon states, in combination with detectors with high efficiency and short dead-time. Current developments are promising, with a reported quantum efficiency of $93\%$ at telecom wavelengths \cite{bib:marsili2013detecting}.

@@

\subsubsection{Distance}

Extending the range of QKD systems is a major challenge and driving factor for QKD in terms of future network applications. Basically, two approaches are being pursued -- free-space and repeaters. A quantum repeater, similar to its classical analogue, is a device that can extend the range of quantum communication between sender and receiver. However, one cannot amplify the signal that contains the quantum information, owing to the no-cloning theorem\index{No-cloning theorem}, which prohibits making copies of unknown quantum states. The fact that an intercept-resend attack by Eve must disrupt the state of the system is the basis for the security of QKD.

A quantum repeater effectively needs to restore the quantum information without measuring it directly, and is a component which is extremely technologically challenging. Over optical fibre networks, the standard loss for 1550nm is 0.2dB/km. Over long enough distances, this unavoidable loss will reduce the key-rate to a level of little practical relevance, therefore a ground-based solution would be to divide the entire channel into segments, where two partners exchange pairs of entangled photons and store it in a quantum memory \cite{bib:PhysRevLett.81.5932, bib:PhysRevA.59.169}.

The second is to use free-space quantum communication techniques via satellite links. Satellite QKD is achievable with  present-day technology. Here satellites are used as intermediate trusted nodes for communication between locations on the ground. Direct links can be established between ground stations and the satellite, thus enabling communication between parties separated by long distances. Satellite QKD suffers less loss, since the effective thickness of the atmosphere is only around 10km when a satellite is directly overhead. In China, satellite QKD over 1200km has been demonstrated \cite{bib:liao2017satellite}.

\subsubsection{Cost \& robustness}

For QKD systems to be consumer-friendly, low cost and robustness are crucial features. Preferably QKD systems should make use of existing data fibre-optic infrastructure since the use of dark fibres are not only expensive, but often unavailable \cite{bib:diamanti2016practical}. Single-photon detectors at room temperatures are also desirable,  because this can remove the requirement for cryogenic cooling, hence reducing power consumption.

@@

Currently, two platforms are being explored: silicon \cite{bib:lim2014review}, and indium phosphide \cite{bib:smit2014introduction}. A reconfigurable QKD system employing an In-P transmitter and silicon detectors has been demonstrated in the laboratory \cite{bib:sibson2017chip}.

@@

In parallel to hardware development, research efforts are being directed at finding new QKD protocols which can outperform existing ones. Two of these are high-dimensional (HD) QKD and the Round-Robin differential phase shift protocol (RR-DPS).

High-dimensional QKD aims at encoding more than one bit in each detected photon, which can increase the information capacity when the photon rate is limited. Security proofs against collective attacks are being developed, and an experiment has demonstrated an information capacity 6.9 bits per coincidence rate at 2.7Mbit/s over 20km \cite{bib:zhong2015photon}.

@@

Although QKD protocols are provably information-theoretically secure, physical implementations often contain imperfections which are not considered in the theoretical model. Attacks can be designed to exploit such imperfections, on either the source or the detectors.

Table.~\ref{tab:attacks} (from \cite{bib:lo2014secure}) summarises some attacks against certain commercial and research systems.

\startnormtable
\begin{table*}[!htbp]
\begin{tabular}{|c|c|c|c|} 
 \hline
 Attack &  Targeted component & Tested system & References\\ 
  \hline
  \hline
Time shift
        & Detector & Commercial & \cite{bib:qi2005time, bib:PhysRevA.78.042333, bib:PhysRevA.74.022313}\\
Time information & Detector & Research & \cite{bib:lamas2007breaking} \\
Detector control & Detector  &   Commercial & \cite{bib:lydersen2010hacking, bib:yuan2010avoiding}\\
Detector control  & Detector  & Research & \cite{bib:gerhardt2011full} \\
Detector dead-time      & Detector  & Research   & \cite{bib:weier2011quantum}      \\
Channel calibration    & Detector  &  Commercial  & \cite{bib:jain2011device}      \\
Phase remapping  &  Phase modulator & Commercial & \cite{bib:xu2010experimental} \\
Phase information & Source & Research & \cite{bib:tang2013source}          \\
Device calibration  & Local oscillator & Research & \cite{bib:jouguet2013preventing} \\
                \hline
\end{tabular}
\caption{\label{tab:attacks} Summary of various attacks against some commercial and 
research QKD systems}
\end{table*}
\startalgtable

To regain security, a number of solutions have been proposed:

\subsubsection{QKD with imperfect sources}

The source is typically less vulnerable to attacks because Alice can prepare her quantum states in a protected environment, and we expect that she can characterise her source. Therefore flaws in the state preparation can be incorporated into the security proof.

Loss-tolerant protocols has been proposed \cite{bib:PhysRevA.90.052314}, and further developed by \cite{bib:PhysRevA.92.032305}, where decoy state\index{Decoy states} QKD with tight finite-key security has been employed. A wide range of imperfections with the laser source has been taken into account in \cite{bib:mizutani2015finite}, including intensity fluctuation. A security proof has shown that perfect phase randomisation is also not necessary \cite{bib:cao2015discrete}.

This provides strong evidence that secure quantum communication with imperfect sources is feasible \cite{bib:diamanti2016practical}. Intuitively, QKD with imperfect sources are feasible, because by assuming that the states prepared by Alice are qubits, then Eve cannot unambiguously discriminate Alice's states \cite{bib:diamanti2016practical}.

\subsubsection{Measurement-device-independent QKD}

To prove security for Bob's measurement device is more problematic, since Eve has complete access to the quantum channel and she can send any signal.

One candidate for a long-term solution to side-channel attacks\index{Side-channel attacks} is device-independent (DI) QKD \cite{bib:PhysRevLett.98.230501}. It relies on the violation of a Bell inequality\index{Bell inequality} \cite{bib:hensen2015loophole}, and the security can be proven without knowledge of the implementation. However, the expected secure key-rate is low even at short distances. A more practical approach is measurement-device independence (MDI) \cite{bib:PhysRevLett.108.130503} QKD, which is immune to side-channel attacks against the measurement device. Here the device is treated as a black box, and does not need to be trusted. An important assumption for MDI QKD is that Eve cannot interfere with the state preparation process.

@@

We have discussed some significant remaining challenges in QKD. These range from theoretical security proofs to hardware developments. Advances in QKD will not only enable point-to-point quantum communication, but have implications for a range of network applications, such as quantum secret sharing \cite{bib:cleve1999share, bib:PhysRevA.61.042311, bib:PhysRevA.71.044301}, blind quantum computing \cite{bib:broadbent2009universal, bib:barz2012demonstration}, quantum anonymous broadcasting \cite{bib:christandl2005quantum}, and many more.

### 2018-10-09 Sections/optical_stability_in_quantum_networks.tex
Minor tweaks, formatting

Such processes are likely to arise in a multitude of ways, including, but certainly not limited to:
\begin{itemize}
	\item Optical fibre: slight variations in temperatures induce refractive index changes, or changes in physical dimension, resulting in temporal displacements of optical wave-packets.
	\item Satellite: precise knowledge of the distance to a rapidly moving target, at the scale of photon wave-packets, is an extremely daunting prospect.
	\item Free space (including via satellite): unpredictable temperature and pressure fluctuations in the atmosphere cause unpredictable variations in the speed of light.
\end{itemize}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{wavepacket} \\
	\captionspacefig \caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.475\textwidth]{MZ_setup} \\
	\includegraphics[width=0.475\textwidth]{MZ}
	\captionspacefig \caption{Mach-Zehnder self-interference of a single photon. (top) Layout of the interferometer. The photon is subject to a time-delay $\tau$ within only the upper arm of a balanced interferometer, comprising two 50:50 beamsplitters. (bottom) Interference fringe $P_\mathrm{MZ}(\tau)$ as a function of the time-delay. The interference is sensitive at the scale of the photon wavelength, (blue) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:MZ_inter}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[width=0.325\textwidth]{HOM_setup} \\
	\includegraphics[width=0.475\textwidth]{HOM}
	\captionspacefig \caption{Hong-Ou-Mandel interference between two independent photons, $A$ and $B$. (top) Layout of the interferometer. Two photons given by mode operators $\hat{A}^\dag$ and $\hat{B}^\dag$\index{Mode operators} (Sec.~\ref{sec:spatio_temporal}), both with temporal distribution function $\psi(t)$, interfere at a 50:50 beamsplitter, where mode $A$ is first subject to a time-delay $\tau$. (bottom) Interference fringe $P_\mathrm{HOM}(\tau)$ as a function of the time-delay. The fringe is only sensitive at the scale of the wave-packet envelope, (orange) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:HOM_inter}
\end{figure}

>>>>

Such processes are likely to arise in a multitude of ways, including, but certainly not limited to:
\begin{itemize}
	\item Optical fibre: slight variations in temperatures induce refractive index changes, or changes in physical dimension, resulting in temporal displacements of optical wave-packets.
	\item Satellite: precise knowledge of the distance to a rapidly moving target, at the scale of photon wave-packets, is an extremely daunting prospect.
	\item Free-space (including via satellite): unpredictable temperature and pressure fluctuations in the atmosphere cause unpredictable variations in the speed of light.
\end{itemize}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{wavepacket} \\
	\captionspacefig \caption{(top) A photonic wave-packet of the form of Eq.~(\ref{eq:wavepacket_modulated}), with Gaussian temporal envelope of width $\sigma$ (orange), shifted by a carrier frequency $\omega_0$ (blue).} \label{fig:HOM_vs_MZ}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{MZ_setup} \\
	\includegraphics[clip=true, width=0.475\textwidth]{MZ}
	\captionspacefig \caption{Mach-Zehnder self-interference of a single photon. (top) Layout of the interferometer. The photon is subject to a time-delay $\tau$ within only the upper arm of a balanced interferometer, comprising two 50:50 beamsplitters. (bottom) Interference fringe $P_\mathrm{MZ}(\tau)$ as a function of the time-delay. The interference is sensitive at the scale of the photon wavelength, (blue) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:MZ_inter}
\end{figure}

@@

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.325\textwidth]{HOM_setup} \\
	\includegraphics[clip=true, width=0.475\textwidth]{HOM}
	\captionspacefig \caption{Hong-Ou-Mandel interference between two independent photons, $A$ and $B$. (top) Layout of the interferometer. Two photons given by mode operators $\hat{A}^\dag$ and $\hat{B}^\dag$\index{Mode operators} (Sec.~\ref{sec:spatio_temporal}), both with temporal distribution function $\psi(t)$, interfere at a 50:50 beamsplitter, where mode $A$ is first subject to a time-delay $\tau$. (bottom) Interference fringe $P_\mathrm{HOM}(\tau)$ as a function of the time-delay. The fringe is only sensitive at the scale of the wave-packet envelope, (orange) in Fig.~\ref{fig:HOM_vs_MZ}.} \label{fig:HOM_inter}
\end{figure}
